---
title: "Homework 1"
author: "Your Name Goes Here"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

### Problem 1
#### Part a)
Whether or not the launch was a success or a failure, and the type of launching agency it was.

#### Part b)
Launching agency is a categorical:nominal. Launch state is categorical:nominal. The number of launches that were a success or a failure is numerical:discrete.

#### Part c)
Explanatory: Type of Launching Agency. Response: Success or Failure

### Problem 2
#### Part a)
Observational study. Study does not alter or give treatment to population.
#### Part b)
Screen time.
#### Part c)
Psychological well-being.
#### Part d)
Good chance, a sample size of n=17,247 is sufficient to draw generalizations.
#### Part e)
Causal relationships cannot be established using correlation.

### Problem 3
#### Part a)
Simple randomized sampling.
#### Part b)
Stratified sampling.
#### Part c)
Cluster sampling.
#### Part d)
Stratified random sampling.
#### Part e)
Convenience sampling.

### Problem 4
#### Part a)
Population: Children between ages 5 and 15
#### Part b)
Might be generalization, but replication studies would be required. Study cannot establish causal relationships.

### Problem 5
#### Part a)
Parameter.
#### Part b)
Sample statistic.
#### Part c)
Sample.
#### Part d)
Variable.

### Problem 6

#### Part a)
$C=2 \pi r$.
$A = \pi r^2$.

#### Part b)
```{r chunk-code-label}
rad <- c(0.25, 1.5)
C <- 2 * pi * rad
```

#### Part c)
The circumferences of circles with radii `r rad` are `r C`.

Example code showing how you can include equations. You will need to replace this with the correct formulas. Can also use \% to get a percent sign in an answer. Note that a single $ is used for an inline equation. A double $$ is used if you want the equation centered on it's own line.

$xy$   $x^2$
$$A = 1/2 \times b \times h$$

### Problem 7
``` {r Read in Patient Data}
# We are providing the code for reading in the data and converting
# Sex and MaritalStat to type factor
PDat <- read_csv("Patient_Data.csv")
# Create a factor variable for Sex; the levels will be in 
# alphabetical order
PDat$Sex <- factor(PDat$Sex)
# Create a factor variable with a specified order to the levels
# of MaritalStat. Marital status is not an ordinal variable, 
# but you can still set the order of the levels to control 
# the order they are printed in output
PDat$MaritalStat <- factor(PDat$MaritalStat,
                           level=c("S","M","D","W"))
############## 
# The code on lines 77 - 79 demonstrate the use of functions 
# you will need for parts a) - c). Copy/paste and edit the code
# as needed for each part of the problem. After you figure out
# the code you need for each part, comment out or remove these 
# lines so they do not clutter up your assignment with extra output.
# PDat %>% count(Sex)
# PDat.F <- PDat %>% filter(Sex == "F")
# glimpse(PDat.F)
```

#### Part a)
```{r count observations in maritial stat}
PDat %>% count(ID)
PDat %>% count(Sex)
PDat %>% count(MaritalStat)
PDat %>% count(Age)
PDat %>% count(Weight)
PDat %>% count(TotChol)
PDat %>% count(SystolicP)
```
#### Part b)
```{r find widowed}
PDat.WIDOWED = PDat %>% filter(MaritalStat == "D")
glimpse(PDat.WIDOWED)
```

#### Part c)
```{r calculate percent widowed female}
nFemaleDivorced <- PDat.WIDOWED %>% filter(Sex =="F") %>% count()
nDivorced <- PDat.WIDOWED %>% count()
percentDivorcedFemale <- nFemaleDivorced / nDivorced
```
`r percentDivorcedFemale` of divorced individuals are female.

### Problem 8
#### Part a)
Observational. The study does not apply a treatment or alter the participants' behavior in an intentional way.
#### Part b)
Individuals with knowlege, either first hand or second hand, of the disease schizophrenia and its connotations.
#### Part c)
Researchers surveyed those familiar with the disease either as a stakeholder or a victim, with n = 1190.
#### Part d)
After being debriefed on the situation, 74% of individuals were in favor of renaming the disease.
#### Part e)
1. Limited querying of minority populations
2. Larger than normal (67%) amount of respondents were female
#### Part f)
To understand where improvements in the study could have been made for future studies to be done.